---
page-layout: custom
toc: false
pagetitle: "Academic CV | Dr. Hasan Sarıcı"
description-meta: "Academic curriculum vitae of Dr. Hasan Sarıcı, including education, research, publications, teaching, and professional experience."
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: cv-setup
source("R/cv_helpers.R")
cv <- load_cv_data()
profile <- cv$profile[1, ]
```

::: {.cv-page}

::: {.cv-hero}
::: {.cv-shell}

::: {.section-kicker}
ACADEMIC CURRICULUM VITAE
:::

# Dr. Hasan Sarıcı

::: {.cv-role}
`r profile$position_en` · `r profile$program_en`
:::

::: {.cv-affiliation}
`r profile$department_en` · `r profile$faculty_en` · `r profile$institution_en`
:::

::: {.cv-contact-row}
[Email](mailto:`r profile$email`){.cv-contact-link}
[ORCID](https://orcid.org/`r profile$orcid`){.cv-contact-link target="_blank" rel="noopener"}
[GitHub](https://github.com/hasansarici3){.cv-contact-link target="_blank" rel="noopener"}
[Institutional Profile](https://egitim.beun.edu.tr/egitim-bilimleri-bolumu/akademik-kadro.html){.cv-contact-link target="_blank" rel="noopener"}
[Publications](publications.qmd){.cv-contact-link}
[Research](research.qmd){.cv-contact-link}
[PDF CV - English](assets/documents/Hasan_Sarici_Academic_CV_EN.pdf){.cv-contact-link target="_blank"}
[PDF CV - Türkçe](assets/documents/Hasan_Sarici_Akademik_CV_TR.pdf){.cv-contact-link target="_blank"}
:::

:::
:::

::: {.cv-section}
::: {.cv-shell}

::: {.section-kicker}
RESEARCH INTERESTS
:::

```{r}
#| results: asis
render_cv_interests(cv$interests, "en")
```

:::
:::

::: {.cv-section .cv-soft}
::: {.cv-shell}

::: {.section-kicker}
ACADEMIC POSITIONS
:::

```{r}
#| results: asis
render_cv_experience(cv$experience, "en")
```

:::
:::

::: {.cv-section}
::: {.cv-shell}

::: {.section-kicker}
EDUCATION
:::

```{r}
#| results: asis
render_cv_education(cv$education, "en")
```

:::
:::

::: {.cv-section .cv-soft}
::: {.cv-shell}

::: {.section-kicker}
RESEARCH PROJECTS
:::

```{r}
#| results: asis
render_cv_projects(cv$projects, "en")
```

:::
:::

::: {.cv-section}
::: {.cv-shell}

::: {.section-kicker}
TEACHING EXPERIENCE
:::

## Undergraduate courses · 2024–2026

```{r}
#| results: asis
render_cv_teaching(cv$teaching, "en")
```

:::
:::

::: {.cv-section .cv-soft}
::: {.cv-shell}

::: {.section-kicker}
PEER-REVIEWED PUBLICATIONS
:::

```{r}
#| results: asis
render_cv_publications(cv$publications, "peer_reviewed", "en")
```

::: {.cv-more-link}
[View all publications →](publications.qmd)
:::

:::
:::

::: {.cv-section}
::: {.cv-shell}

::: {.section-kicker}
MANUSCRIPTS IN THE PUBLICATION PIPELINE
:::

```{r}
#| results: asis
render_cv_publications(cv$publications, "under_review", "en")
```

:::
:::

::: {.cv-section .cv-soft}
::: {.cv-shell}

::: {.section-kicker}
BOOKS & BOOK CHAPTERS
:::

```{r}
#| results: asis
render_cv_publications(cv$publications, "books", "en")
```

:::
:::

::: {.cv-section}
::: {.cv-shell}

::: {.section-kicker}
INTERNATIONAL RESEARCH NETWORKS
:::

```{r}
#| results: asis
render_cv_networks(cv$networks)
```

:::
:::

::: {.cv-section .cv-soft}
::: {.cv-shell}

::: {.section-kicker}
CERTIFICATIONS & PROFESSIONAL TRAINING
:::

```{r}
#| results: asis
render_cv_professional(cv$professional, "certification", "en")
```

:::
:::

::: {.cv-section}
::: {.cv-shell}

::: {.section-kicker}
SPORT & COACHING EXPERIENCE
:::

```{r}
#| results: asis
render_cv_professional(cv$professional, "coaching", "en")
```

:::
:::

::: {.cv-section .cv-soft}
::: {.cv-shell}

::: {.cv-two-column}

:::
### Languages

```{r}
#| results: asis
render_cv_professional(cv$professional, "language", "en")
```
:::

:::
### Technical & Methodological Skills

```{r}
#| results: asis
render_cv_professional(cv$professional, "skill", "en")
```
:::

:::
:::
:::

:::
