---
page-layout: custom
toc: false
description: "Research, academic work, and professional activities of Dr. Hasan Sarıcı."
pagetitle: "Dr. Hasan Sarıcı | Researcher, Psychological Counsellor and Academic"
description-meta: "Research, publications, projects, and academic work of Dr. Hasan Sarıcı."
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: homepage-publications
source("R/publications_helpers.R")
publications <- read_publications("data/publications.csv")
```

<style>
.hero-split {
  display: grid;
  grid-template-columns: minmax(0, 1.45fr) minmax(280px, 0.9fr);
  gap: clamp(1.75rem, 3vw, 3.25rem);
  align-items: center;
}
.hero-main { min-width: 0; }
.hero-portrait-wrap {
  display: flex;
  justify-content: center;
  align-items: center;
}
.hero-portrait {
  display: block;
  width: min(100%, 420px);
  aspect-ratio: 4 / 5;
  object-fit: cover;
  border-radius: 28px;
  box-shadow: 0 26px 60px rgba(15, 23, 42, 0.16);
  border: 1px solid rgba(15, 23, 42, 0.08);
  background: #ffffff;
}
@media (max-width: 980px) {
  .hero-split { grid-template-columns: 1fr; }
  .hero-portrait-wrap { order: -1; margin-bottom: 0.5rem; }
  .hero-portrait { width: min(100%, 320px); }
}
@media (max-width: 640px) {
  .hero-portrait { width: min(100%, 280px); border-radius: 22px; }
}
</style>

::: {.home-page}

::: {.home-hero}
::: {.home-shell}

::: {.hero-split}

::: {.hero-main}
::: {.hero-eyebrow}
PSYCHOLOGY · RESEARCH · PRACTICE
:::

# Dr. Hasan Sarıcı

::: {.hero-role}
**Researcher · Psychological Counsellor · Academic**
:::

::: {.hero-affiliation}
**Guidance and Psychological Counseling Program** · Department of Educational Sciences · Ereğli Faculty of Education · Zonguldak Bülent Ecevit University
:::

::: {.hero-lead}
I study psychological processes in relation to the environmental, cultural, and sporting contexts in which they unfold.
:::

::: {.hero-copy}
My work focuses on climate anxiety, psychological mechanisms, pro-environmental outcomes, cross-cultural psychology, and sport and football psychology. Across these areas, I prioritise methodological rigour, open and reproducible science, and research with meaningful practical implications.
:::

::: {.hero-profile-links}
[ORCID ↗](https://orcid.org/0000-0001-8017-2694)
[GitHub ↗](https://github.com/hasansarici3)
[Email](mailto:hasansarici3@gmail.com)
:::

::: {.hero-actions}
[Explore My Research](research.qmd){.home-button .home-button-primary}
[Publications](publications.qmd){.home-button}
[CV](cv.qmd){.home-button .home-button-quiet}
:::
:::

::: {.hero-portrait-wrap}
<img src="assets/images/hasan-home-portrait.svg" class="hero-portrait" alt="Portrait of Dr. Hasan Sarıcı">
:::

:::

:::
:::

::: {.home-section}
::: {.home-shell}

::: {.section-kicker}
RESEARCH FOCUS
:::

## Understanding psychological processes in context

::: {.section-intro}
My research programme develops around four interconnected lines examining psychological processes across environmental, social, educational, and performance contexts.
:::

::: {.focus-grid .focus-grid-four}

::: {.focus-card}
### Climate & Environmental Psychology

Climate anxiety, climate emotions, psychological responses to environmental threats, and pro-environmental behaviour.

[Explore this research →](research.qmd)
:::

::: {.focus-card}
### Psychological Counselling & Education

Poverty-sensitive counselling, trauma-informed education, psychosocial support, and inclusive school contexts.

[Explore this research →](research.qmd)
:::

::: {.focus-card}
### Digital Behaviour & Emotion Regulation

Cyberbullying, digital citizenship, interpersonal processes, and adaptive or maladaptive emotion-regulation patterns.

[Explore this research →](research.qmd)
:::

::: {.focus-card}
### Sport & Performance Psychology

Psychological functioning in athletes, performance, mindfulness-based interventions, and football psychology.

[Explore this research →](research.qmd)
:::

:::
:::
:::

::: {.home-section .featured-section}
::: {.home-shell}

::: {.section-kicker}
SELECTED PUBLICATIONS
:::

## Recent peer-reviewed work

::: {.section-intro}
A selection of my recent peer-reviewed publications. Visit the Publications page for the complete publication record.
:::

```{r}
#| results: asis
render_featured_publications(publications, lang = "en", n = 3)
```

::: {.featured-publications-all}
[View all publications →](publications.qmd)
:::

:::
:::

::: {.home-section .approach-section}
::: {.home-shell}

::: {.section-kicker}
RESEARCH APPROACH
:::

## I focus not only on findings, but also on the quality of the research process.

::: {.approach-grid}

::: {.approach-item}
**01 — Methodological rigour**

Strong research designs, transparent analytical decisions, and appropriate statistical methods.
:::

::: {.approach-item}
**02 — Open and reproducible science**

Research workflows, analytical code, and scientific outputs designed to be as transparent and reproducible as possible.
:::

::: {.approach-item}
**03 — Knowledge with practical value**

Translating scientific findings into meaningful applications for psychological practice, society, and performance settings.
:::

:::
:::
:::

::: {.home-cta}
::: {.home-shell .cta-inner}

::: {.cta-copy}
### Explore my work in more detail

Browse publications, projects, and research areas across the website.
:::

::: {.cta-actions}
[Projects](projects.qmd){.home-button .home-button-light}
[Contact](contact.qmd){.home-button .home-button-outline-light}
:::

:::
:::

:::
