---
page-layout: custom
toc: false
pagetitle: "Projects | Dr. Hasan Sarıcı"
description-meta: "Ongoing and completed research projects of Dr. Hasan Sarıcı."
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: projects-setup
source("R/projects_helpers.R")
projects <- read_projects("data/projects.csv")
project_stats <- project_counts(projects)
```

::: {.projects-page}

::: {.projects-hero}
::: {.projects-shell}

::: {.section-kicker}
PROJECTS
:::

# Research projects connecting evidence with practice

::: {.projects-lead}
My research projects examine psychosocial processes, educational environments, and psychological functioning within real-world contexts.
:::

::: {.project-stats}

::: {.project-stat}
`r project_stats$total`

**Recorded projects**
:::

::: {.project-stat}
`r project_stats$ongoing`

**Ongoing**
:::

::: {.project-stat}
`r project_stats$completed`

**Completed**
:::

::: {.project-stat}
`r project_stats$externally_funded`

**Externally funded**
:::

:::
:::
:::

::: {.projects-section}
::: {.projects-shell}

::: {.section-kicker}
ONGOING
:::

## Current research projects

```{r}
#| results: asis
render_projects(
  projects,
  status = "ongoing",
  lang = "en"
)
```

:::
:::

::: {.projects-section .projects-soft}
::: {.projects-shell}

::: {.section-kicker}
COMPLETED
:::

## Previous research projects

```{r}
#| results: asis
render_projects(
  projects,
  status = "completed",
  lang = "en"
)
```

:::
:::

::: {.projects-cta}
::: {.projects-shell .projects-cta-inner}

::: {.projects-cta-copy}
### Connected research outputs

Explore publications arising from these and other strands of my research programme on the Publications page.
:::

::: {.projects-cta-actions}
[Publications](publications.qmd){.home-button .home-button-light}
[Research](research.qmd){.home-button .home-button-outline-light}
:::

:::
:::

:::
