---
page-layout: custom
toc: false
pagetitle: "Publications | Dr. Hasan Sarıcı"
description-meta: "Peer-reviewed publications, manuscripts in the publication pipeline, and book contributions by Dr. Hasan Sarıcı."
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: publications-setup
source("R/publications_helpers.R")
publications <- read_publications("data/publications.csv")
pub_counts <- publication_counts(publications)
```

::: {.publications-page}

::: {.publications-hero}
::: {.publications-shell}

::: {.section-kicker}
PUBLICATIONS
:::

# Research outputs

::: {.publications-lead}
Peer-reviewed articles, manuscripts in the publication pipeline, and book contributions are generated from a single sustainable research database.
:::

::: {.publication-stats}

::: {.publication-stat}
`r pub_counts$peer_reviewed`

**Peer-reviewed articles**
:::

::: {.publication-stat}
`r pub_counts$under_review`

**Publication pipeline**
:::

::: {.publication-stat}
`r pub_counts$books`

**Books / chapters**
:::

:::

::: {.publications-orcid}
[ORCID: 0000-0001-8017-2694](https://orcid.org/0000-0001-8017-2694){target="_blank"}
:::

:::
:::

::: {.publications-section}
::: {.publications-shell}

::: {.section-kicker}
PEER-REVIEWED WORK
:::

## Published articles

```{r}
#| results: asis
render_publications(
  publications,
  category = "peer_reviewed",
  lang = "en"
)
```

:::
:::

::: {.publications-section .publications-soft}
::: {.publications-shell}

::: {.section-kicker}
CURRENT PUBLICATION PIPELINE
:::

## Submitted, in-review, or revising manuscripts

::: {.publications-note}
This section reports unpublished manuscripts conservatively. “Submitted / in editorial process,” “in peer review,” and “revision / preparing resubmission” are shown as distinct statuses and are updated in the underlying database as editorial circumstances change.
:::

```{r}
#| results: asis
render_publications(
  publications,
  category = "under_review",
  lang = "en"
)
```

:::
:::

::: {.publications-section}
::: {.publications-shell}

::: {.section-kicker}
BOOKS & BOOK CHAPTERS
:::

## Other academic publications

```{r}
#| results: asis
render_publications(
  publications,
  category = "books",
  lang = "en"
)
```

:::
:::

:::
