---
format:
  typst:
    papersize: a4
    margin:
      top: 14mm
      bottom: 14mm
      left: 16mm
      right: 16mm
    fontsize: 9pt
    linestretch: 1.05
    page-numbering: "1"
execute-dir: project
execute:
  echo: false
  warning: false
  message: false
lang: en
title-meta: "Dr. Hasan Sarıcı - Academic Curriculum Vitae"
author-meta: "Hasan Sarıcı"
---

```{r}
#| label: setup
source("R/cv_pdf_helpers.R")
cv <- pdf_cv_data()
p <- cv$profile[1, ]
```

# Hasan Sarıcı, PhD

**`r p$position_en`**  
`r p$program_en`  
`r p$department_en`  
`r p$faculty_en`  
`r p$institution_en`

`r p$email` · [hasansarici.com](https://hasansarici.com) · ORCID: `r p$orcid`


## Research Interests

```{r}
#| results: asis
pdf_interests(cv$interests, "en")
```

## Academic Positions

```{r}
#| results: asis
pdf_experience(cv$experience, "en")
```

## Education

```{r}
#| results: asis
pdf_education(cv$education, "en")
```

## Research Projects

```{r}
#| results: asis
pdf_projects(cv$projects, "en")
```


```{=typst}
#pagebreak()
```

## Courses Taught

**Undergraduate level, 2024-2026**

```{r}
#| results: asis
pdf_teaching(cv$teaching, "en")
```

## Peer-Reviewed Publications

```{r}
#| results: asis
pdf_publications(cv$publications, "peer_reviewed", "en")
```

## Manuscripts in the Publication Pipeline

```{r}
#| results: asis
pdf_publications(cv$publications, "under_review", "en")
```



## Books and Book Chapters

```{r}
#| results: asis
pdf_publications(cv$publications, "books", "en")
```


```{=typst}
#pagebreak()
```

## International Research Networks

```{r}
#| results: asis
pdf_networks(cv$networks)
```

## Selected Conference Presentations

### International Conferences

```{r}
#| results: asis
pdf_conferences(cv$conferences, "international")
```

### National Conferences

```{r}
#| results: asis
pdf_conferences(cv$conferences, "national")
```

## Certifications and Professional Training

```{r}
#| results: asis
pdf_professional(cv$professional, "certification", "en")
```

## Sport and Coaching Experience

```{r}
#| results: asis
pdf_professional(cv$professional, "coaching", "en")
```

## Professional Membership

```{r}
#| results: asis
pdf_professional(cv$professional, "membership", "en")
```

## Languages

```{r}
#| results: asis
pdf_professional(cv$professional, "language", "en")
```

## Technical and Methodological Skills

```{r}
#| results: asis
pdf_professional(cv$professional, "skill", "en")
```
